For induction-induction, induction is enough

### 2019-08-30 paper/paper.tex
related work

@@

@@

\section{Constructing all IITs from the theory of signatures}
\label{sec:andras}

Show using the CwF model that the existence of the theory of IIT
signatures (Section \ref{sec:theory_of_signatures}) entails the
existance of all IITs.

>>>>

This is the paper version of our TYPES 2019 talk.

\subsection{Related work}

Reduction of classes of inductive types: reduce indexed W-types to
W-types. IR types to indexed types. IITs were introduced by
Forsberg. What he did.  QIITs by Forsberg-lots of people. Our QIIT
paper. Jakob TYPES 2019 abstract.  Jasper Huguin: he didn't do
recursion-recursion. Without UIP.

Similar techique for other type theories: Streicher. Initiality
project, Brunerie. These all use quotients. Closest: Lafont TYPES
abstract 2017. Does not use quotients.

Constructing intrinsic syntax but different techniques: Chapman,
Danielsson, Nuo. These use induction-induction which is our goal.

@@

\subsection{Formalisation}

UIP, funext, rewrite rules, version of Agda.

@@

\section{Constructing all IITs from the theory IIT of signatures}
\label{sec:andras}

Explain that the previous paper was modular.

\section{Further work}

Infinitary, explain why it is difficult. Without UIP, without funext,
for QIITs (in the setoid model).
